Sexual selection improves population fitness: a systematic review and meta-analysis

### 2019-01-03 meta_analysis_sexual_selection_pop_fitness.Rmd
updated supp info

---
title: 'Sexual selection improves population fitness: a meta-analysis'
author: "Justin G. Cally^1^, Devi Stuart-Fox^1^ and Luke Holman^1^ <br></br> <br></br> ^1^The University of Melbourne"
subtitle: Supplementary Material
bibliography: bibliography_meta_analysis.bib
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
  pdf_document: default
---

@@

```{r, warning = FALSE, message=FALSE, error = FALSE}
if(!file.exists("data/grand.mean.class.bayes.rds")){
  grand.mean.class.bayes <- brm(g | se(SE)  ~ Outcome.Class # Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                          + (1|Study.ID)
                          + (1|Taxon), 
                          family = "gaussian", 
                          seed = 1,
                          cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                          control = list(adapt_delta = 0.9999, max_treedepth = 15),
                          data = full_dataset %>% mutate(SE = sqrt(var.g)))

@@

```{r, message=FALSE, error = FALSE, warning=FALSE}
# strict_dataset <- full_dataset %>% 
#   filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated")  %>% 
#   mutate(Sex = relevel(Sex, ref = "M"),
#          Environment = relevel(factor(Environment), ref = "Unstressed"),
#          Taxon = relevel(factor(Taxon), ref = "Beetle"))

strict_dataset <- full_dataset %>% 
  filter(Outcome.Class == "Direct" & Environment != "Not Stated")  %>% 
  mutate(Sex = relevel(Sex, ref = "M"),
         Environment = relevel(factor(Environment), ref = "Unstressed"),
         Taxon = relevel(factor(Taxon), ref = "Beetle"))

model.complete <- rma.mv(g, V = var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon + Enforced.Monogamy, 
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = strict_dataset)

@@

```{r, warning=FALSE, fig.height= 8, fig.width=8}
# function that makes predict.rma work like a normal predict() function, instead of the idiosyncratic way that it works by default.
get.predictions.complete <- function(newdata){
  B<-0; F<-0; Stressed<-0; Cricket<-0; Fly<-0; Guppy<-0; Mite<-0; Mouse<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Stressed<-1
  if(newdata[3] == "Cricket") Cricket<-1
  if(newdata[3] == "Fly") Fly<-1
  if(newdata[3] == "Guppy") Guppy<-1
  if(newdata[3] == "Mite") Mite<-1
  if(newdata[3] == "Mouse") Mouse<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, 1, interaction1, interaction2))
}
# Get the predictions for each combination of moderators
predictions.complete <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed"),
                           Taxon = c("Beetle", "Cricket", "Fly", "Guppy", "Mite", "Mouse")))
predictions.complete <- cbind(predictions.complete, do.call("rbind", apply(predictions.complete, 1, get.predictions.complete))) %>%
  select(Sex, Environment, Taxon, pred, se, ci.lb, ci.ub) 
for(i in 4:7) predictions.complete[,i] <- unlist(predictions.complete[,i])

@@

```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
if(!file.exists("data/brms.complete2.rds")){
  brms.complete2 <- brm(g | se(SE)  ~ 1 + Sex * Environment 
                        + (1|Taxon) 
                        + (1|Study.ID) 
                        + (1|Outcome), 
                        family = "gaussian", 
                        seed = 1,
                        cores = 4, chains = 4, iter = 4000, 
                        control = list(adapt_delta = 0.9999, max_treedepth = 15),
                        data = strict_dataset %>% mutate(SE = sqrt(var.g)))
  saveRDS(brms.complete2, file = "data/brms.complete2.rds")
}
brms.complete2 <- readRDS(file = "data/brms.complete2.rds") 
```
<br></br>

@@

if(!file.exists("data/lnRR.brms.env.sex.rds")){
  lnRR.brms.env.sex <- brm(lnRR | se(SE)  ~ 1 + Sex * Environment 
                        + (1|Taxon) 
                        + (1|Study.ID) 
                        + (1|Outcome), 
                        family = "gaussian", 
                        seed = 1,
                        cores = 4, chains = 4, iter = 4000, 
                        control = list(adapt_delta = 0.9999, max_treedepth = 15),
                        data = lnRR.data %>% mutate(SE = sqrt(lnRR_var)) %>% 
                          filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
  saveRDS(lnRR.brms.env.sex, file = "data/lnRR.brms.env.sex.rds")
}
lnRR.brms.env.sex <- readRDS(file = "data/lnRR.brms.env.sex.rds")

>>>>

---
title: 'Sexual selection improves population fitness: a systematic review and meta-analysis'
author: "Justin G. Cally^1^, Devi Stuart-Fox^1^ and Luke Holman^1^ <br></br> <br></br> ^1^The University of Melbourne"
subtitle: Supplementary Material
bibliography: bibliography_meta_analysis.bib
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
  pdf_document: default
---

@@

```{r, warning = FALSE, message=FALSE, error = FALSE}
if(!file.exists("data/grand.mean.class.bayes.rds")){
  grand.mean.class.bayes <- brm(g | se(SE)  ~ Outcome.Class # Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                          + (1|Study.ID)
                          + (1|Taxon), 
                          family = "gaussian", 
                          seed = 1,
                          cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                          control = list(adapt_delta = 0.999, max_treedepth = 15),
                          data = full_dataset %>% mutate(SE = sqrt(var.g)))

@@

```{r, message=FALSE, error = FALSE, warning=FALSE}
strict_dataset <- full_dataset %>%
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated")  %>%
  mutate(Sex = relevel(Sex, ref = "M"),
         Environment = relevel(factor(Environment), ref = "Unstressed"),
         Taxon = relevel(factor(Taxon), ref = "Beetle"))

# strict_dataset <- full_dataset %>% 
#   filter(Outcome.Class == "Direct" & Environment != "Not Stated")  %>% 
#   mutate(Sex = relevel(Sex, ref = "M"),
#          Environment = relevel(factor(Environment), ref = "Unstressed"),
#          Taxon = relevel(factor(Taxon), ref = "Beetle"))

model.complete <- rma.mv(g, V = var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon, 
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = strict_dataset)

@@

```{r, warning=FALSE, fig.height= 8, fig.width=8}
# function that makes predict.rma work like a normal predict() function, instead of the idiosyncratic way that it works by default.
get.predictions.complete <- function(newdata){
  B<-0; F<-0; Stressed<-0; Cricket<-0; Fly<-0; Guppy<-0; Mite<-0; Mouse<-0; interaction1<-0; interaction2<-0;
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Stressed<-1
  if(newdata[2] == "Cricket") Cricket<-1
  if(newdata[3] == "Fly") Fly<-1
  if(newdata[3] == "Guppy") Guppy<-1
  if(newdata[3] == "Mite") Mite<-1
  if(newdata[3] == "Mouse") Mouse<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, interaction1, interaction2))
}
# Get the predictions for each combination of moderators
predictions.complete <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed"),
                           Taxon = c("Beetle", "Cricket", "Fly", "Guppy", "Mite", "Mouse")))
predictions.complete <- cbind(predictions.complete, do.call("rbind", apply(predictions.complete, 1, get.predictions.complete))) %>%
  select(Sex, Environment, Taxon, pred, se, ci.lb, ci.ub) 
for(i in 4:7) predictions.complete[,i] <- unlist(predictions.complete[,i])

@@

```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
if(!file.exists("data/brms.complete2.rds")){
  brms.complete2 <- brm(g | se(SE)  ~ 1 + Sex * Environment 
                        + (1|Taxon) 
                        + (1|Study.ID) 
                        + (1|Outcome), 
                        family = "gaussian", 
                        seed = 1,
                        cores = 4, chains = 4, iter = 4000, 
                        control = list(adapt_delta = 0.999, max_treedepth = 15),
                        data = strict_dataset %>% mutate(SE = sqrt(var.g)))
  saveRDS(brms.complete2, file = "data/brms.complete2.rds")
}
brms.complete2 <- readRDS(file = "data/brms.complete2.rds") 
```
<br></br>

@@

if(!file.exists("data/lnRR.brms.env.sex.rds")){
  lnRR.brms.env.sex <- brm(lnRR | se(SE)  ~ 1 + Sex * Environment 
                        + (1|Taxon) 
                        + (1|Study.ID) 
                        + (1|Outcome), 
                        family = "gaussian", 
                        seed = 1,
                        cores = 4, chains = 4, iter = 4000, 
                        control = list(adapt_delta = 0.999, max_treedepth = 15),
                        data = lnRR.data %>% mutate(SE = sqrt(lnRR_var)) %>% 
                          filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
  saveRDS(lnRR.brms.env.sex, file = "data/lnRR.brms.env.sex.rds")
}
lnRR.brms.env.sex <- readRDS(file = "data/lnRR.brms.env.sex.rds")
